---
title: "World Happiness Report Analysis"
output: html_document
    theme: flatly
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Background 



# Research Questions

I've developed research questions for this project aimed at understanding the relationships between different variables and overall happiness score. 

**Question 1:** Which factors are the strongest predictors of a country’s happiness score?

**Question 2:** How well do health indicators predict happiness scores compared to economic indicators? 

**Question 3:** How is public health expenditure associate with happiness score across countries and years?

**Question 4:** Do countries with higher public health expenditure also show higher healthy life expectancy?

# Loading Necessary Packages 

```{r}
library(tidyverse)
library(ggcorrplot)
library(broom)
library(lubridate)
```

# Importing data

I downloaded the data for this project from [Kaggle](https://www.kaggle.com/datasets/khushikyad001/world-happiness-report/data). I'll use the `read.csv` function to import it. 




